\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage{cmbright}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage[sf]{libertine}
\usepackage{microtype}
\usepackage{paracol}
\usepackage{supertabular}
\usepackage{titlesec}
\hypersetup{colorlinks, urlcolor=black, linkcolor=black}

% Custom Commands

% Geometry
\geometry{hmargin=1.5cm, vmargin=1cm}
\columnratio{0.7, 0.3}
\setlength\columnsep{0.05\textwidth}
\setlength\parindent{0pt}
\setlength{\smallskipamount}{8pt plus 3pt minus 3pt}
\setlength{\medskipamount}{16pt plus 6pt minus 6pt}
\setlength{\bigskipamount}{24pt plus 8pt minus 8pt}

% Style
\pagestyle{empty}
\titleformat{\section}{\scshape\LARGE\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{\bigskipamount}{\smallskipamount}
\newcommand{\heading}[2]{\centering{\sffamily\Huge #1}\\\smallskip{\large{#2}}}
\newcommand{\entry}[4]{{{\textbf{#1}}} \hfill #3 \\ #2 \hfill #4}
\newcommand{\tableentry}[3]{\textsc{#1} & #2\expandafter\ifstrequal\expandafter{#3}{}{\\}{\\[6pt]}}

\begin{document}


\begin{paracol}{2}

% Name & headline
\heading{Arnab Dhar}
\switchcolumn

% Contact
\begin{itemize}[itemsep=1pt,label={}]
  \item \href{https://wa.me/9163279081}{(+91) 9163279081}
  \item \href{mailto:arnabdhar32@gmail.com}{arnabdhar32@gmail.com}
\end{itemize}

\switchcolumn*


% START: Experience Block

\section{experience}

% COMPANY: Pitangent
\entry{\href{https://in.linkedin.com/company/pitangent}{Pitangent Analytics \& Technology Solutions}}{\emph{Data Scientist}}{Kolkata}{\emph{Jun, 2023 - Present}}
\begin{itemize}
    \item Trained NLP and generative models like BERT, Llama, and Mistral on AWS Sagemaker for sentiment analysis, chatbots, and RAG applications.
    \item Deployed chatbots using OpenAI, Anthropic, and Amazon Bedrock with LLM monitoring via LangSmith, OpenTelemetry, and Grafana.
    \item Conducted R\&D for clients on image generation, LLM quantization, and resource-efficient LLM training.
\end{itemize}

% COMPANY: Pitangent

\medskip

% COMPANY: Vitwo
\entry{\href{https://www.linkedin.com/company/vitwo}{ViTWO}}{\emph{Associate Data Scientist}}{Kolkata}{\emph{Nov, 2021 - Jun, 2023}}
\begin{itemize}
  \item Developed ETL pipelines in Azure Data Factory to connect MySQL and MongoDB with backend applications and PowerBI.
  \item Trained and deployed computer vision and document extraction models, including YOLOv8, TrOCR, and LayoutLM.
\end{itemize}

% COMPANY: Vitwo

% END: Experience Block

\switchcolumn

% START: Skills
\section{skills}
\begin{itemize}[itemsep=1pt,label={\faCode}]
  \item Python
  \item Pytorch
  \item AutoML
  \item LangChain
  \item Grafana Stack
  \item Docker
  \item AWS
  \item Azure
\end{itemize}

% END: Skills

% START: Projects
\switchcolumn

\section{projects}

\entry{HR Chatbot}{Simplified Communications with HRD}{\emph{LangChain, Huggingface, Docker}}{2023-2024}
\begin{itemize}
  \item Trained Llama2 model to answer common HR related queries for both Employees and HR people.
  \item Integrated OpenAI's function calling for advanced tasks like leave requests and reimbursements.
\end{itemize}

\entry{vitwo.ai}{ERP driven by AI}{\emph{Python, Azure, PyTorch}}{2021 - 2023}
\begin{itemize}
  \item Product Page: \href{https://vitwo.ai}{https://vitwo.ai}
  \item Developed seamless ETL pipelines on Azure Datafactory improving efficiency of development cycles.
  \item Developed a document extraction system to automate data extraction from sales invoices, credit notes, and purchase bills.
\end{itemize}
% END: Projects



% START: Education
\switchcolumn
\begin{flushleft}
\section{education}

\entry{\href{https://www.bhu.ac.in/Site/Home/1_2_16_Main-Site}{Banaras Hindu University}}{\emph{M. Sc. Statistics}}{}{2018 - 2020}
\medskip

\entry{\href{https://caluniv.ac.in/}{University of Calcutta}}{\emph{B. Sc. (Hons) Statistics}}{}{2015 - 2018}

\end{flushleft}
% END: Education

% START: Public Links
% \switchcolumn
\section{public links}

\begin{itemize}[itemsep=1pt]
  \item[\faLinkedin] \href{https://www.linkedin.com/in/arnab-dhar}{/arnab-dhar}
  \item[\faGithub] \href{https://www.github.com/arnabd64}{/arnabd64} 
  \item[\faLink] \href{https://hf.co/arnabdhar}{Huggingface} 
\end{itemize}

% END: Public Links

\end{paracol}
\end{document}